%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer \& C++ Server Development Engineer} % Job title
{Seeta Technology Co., Ltd} % Organization
{Peking, China} % Location
{June. 2017 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a }
\item {}
\item {}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Designer \& Programmer} % Job title
{2016 ASABE Robotics Student Design Competition} % Organization
{Orlando, USA} % Location
{July. 2016} % Date
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Responsible for the design and programming of a fully automated robotic system that can simulate the transfer of fruits from the harvester to the processing plant.}
\item{Developed the control system on Arduino Mega 2560.}
\item{Realized the vision system in C++ with OpenCV on Raspberry 3 Model B.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Designer \& Programmer} % Job title
{the First National Intelligent Agricultural Equipment Innovation Competition for College Students} % Organization
{Jiangsu, China} % Location
{Dec. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for the design and programming of a fully automated robotic system that can simulate the tractor’s traversing in field.}
\item {Won the 2nd prize in the competition.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Researcher for <Desktop Application for Processing Plant’s Point Cloud Data>} % Job title
{Undergraduate Research, Institute of Biosystem Automation and Information Technology(Prof. Yong He)} % Organization
{Zhejiang University, Hangzhou, China} % Location
{Feb. 2016- June. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for the Graphical User Interface and several function modules of the application like leaf area measurement, plant’s height measurement.}
\item {Developed the Graphical User Interface in C++ with Qt and the processing function modules with PCL.}
\item {Provided the application to producers and scientists for processing the plant’s point cloud data with ease and speed.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Researcher for <Modeling Microbial Diversity of Anaerobic Digestion through STELLA>} % Job title
{Undergraduate Research Internship, Bhalerao Lab(Prof. Kaustubh Bhalerao)} % Organization
{University of Illinois at Urbana-Champaign, USA} % Location
{July. 2015-Aug. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for a methodology to account for microbial diversity in complex but structured models and the resulting model remains powerful in representing macroscopic experimental data, but is moreover able to get insight in underlying microscopy.}
\item {Adaptation of microorganisms to perturbations and inhibitory substances, as suggested in this model, can significantly improve anaerobic digestion process and thereby wastewater treatment efficiency.}
\item {Constructed the visual mathematical model with tool of STELLA.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}